An Integral-field Spectroscopic Study of Low-power Radio Galaxies

### 2020-08-11 paper.tex
Investigated redshift uncert using VIMOS_analysis/mcmc.py
Mostly work on absorption line and stellar population sections

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Key characteristics of our Southern Sample galaxies.}
    \label{tab:sample}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c l}
      \hline
      \hline
      Host galaxy & Radio source & Redshift & $S_\text{1.4\,GHz}$ & $m_K$ & Dust morphology\\
                  & (PKS) & & (mJy) & (mag) &\\
      \hline 
      ESO~443-G024 & 1258-321 & $0.01703$ & $1387\pm45$ & $8.51$ & no dust$^\text{a}$\\ 
      IC~1459 & 2254-367 & $0.00565$ & $1280\pm45$ & $6.81$ & dust lane$^\text{b}$\\
      IC~1531 & 0007-325 & $0.02553$ & $\leavevmode\phantom{0}388\pm12$ & $9.55$ & --\\
      IC~4296 & 1333-\leavevmode\phantom{0}33 & $0.01248$	& $1342\pm41$ & $7.50$ & edge-on disc$^\text{b}$\\
      NGC~612 & 0131-\leavevmode\phantom{0}36 & $0.02954$ & $\leavevmode\phantom{0}585\pm18$ & $9.58$ & dust lane$^\text{c}$\\
      NGC~1316 & 0320-\leavevmode\phantom{0}37 & $0.00591$ & $\leavevmode\phantom{0}255\pm10$ & $5.59$ & dust patches$^\text{b}$\\
      NGC~1399 & 0336-\leavevmode\phantom{0}35 & $0.00472$ & $\leavevmode\phantom{0}209\pm\leavevmode\phantom{0}7$ & $6.31$ & no dust$^\text{b}$\\
      NGC~3100 & 0958-314	& $0.00879$ & $\leavevmode\phantom{0}530\pm16$ & $8.08$ & dust lane$^\text{d}$\\
      NGC~3557 & 1107-372 & $0.01016$ & $\leavevmode\phantom{0}484\pm16$ & $7.20$ & face-on disc$^\text{b}$\\
      NGC~7075 & 2128-388 & $0.01819$ & $\leavevmode\phantom{0}837\pm28$ & $9.56$ & --\\
      -- & 0718-\leavevmode\phantom{0}34 & $0.02897$ & $1119\pm41$ & $9.97$ & dust patches$^\text{e}$\\
      \hline
      \hline
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: radio source name from the Parkes Southern
      Radio Source Catalogue (PKS). We hereafter refer to the last
      galaxy by its PKS name only. Col.~3: redshift. Col.~4: National
      Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
      $1.4$~GHz flux density \citep{Condon1998}. Col.~5: Two Micron
      All Sky Survey (2MASS) $K$-band apparent magnitude (with
      uncertainties of $\pm0.025$~mag;
      \citealt{Skrutskie2006}). Col.~6: dust morphology from (a)
      \citet{Govoni2000}, (b) \citet{Lauer2005}, (c)
      \citet{Bettoni2001}, (d) \citet{Sandage1979} and (e)
      \citet{Colbert2001}.}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

In each bin, using the measured absorption line strengths, we identify
the best-fitting single stellar population (SSP) model from an
interpolated grid of models using \textsc{emcee}, a \textsc{python}
affine-invariant Markov-chain Monte-Carlo (MCMC) fitting package
\citep{Foreman-Mackey2013}. This grid is created by linearly
interpolating between the models of \citeauthor{Thomas2010}
(\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The
\citetalias{Thomas2010} models are chosen because they are based on
high-resolution flux-calibrated spectra, and therefore do not require
the absorption line strength measurements to be in the Lick/IDS
system.

@@

We find $5$ out of $11$ galaxies, or $45\pm13\%$, are slow rotators
(see Fig.~\ref{fig:lambdaR_ellip}). This fraction is between that of
the Atlas$^\text{3D}$ and MASSIVE surveys, that find respectively
\added{$13\pm2\%$} and \added{$80\pm6\%$} of their sample galaxies to be slow
rotators. {\bf (Again, better to also quote the uncertainties on those
  two fractions. I doubt the decimal place is meaningful in either of
  them.)} As in the regular-/non-regular-rotator classification scheme
(Section~\ref{subsec:RR-NRR}), slow rotators are more likely to be
found in higher mass galaxies, and the three samples
(Atlas$^\text{3D}$, MASSIVE and our Southern Sample) have very
different mass distributions (see the upper panel of
Fig.~\ref{fig:SRmassFraction}).

@@

We find a very large offset between the G4300 index measurements of
\citet{Rampazzo2005} and ours. This index is however extremely
sensitive to the stellar velocity dispersion correction, and we
measure an average difference of the stellar velocity dispersions
measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$. This may
be enough to account for the offset of the measurements. {\bf (Why not
  check this by changing the stellar velocity dispersions used in your
  corrections to those of \citealt{Rampazzo2005}? Check.)}

The offsets of our Fe5015 index measurements are also relatively large
when compared to the measurements of \citet{Rampazzo2005} and
\citet{Vazdekis2010}. The origin of this offset is unclear for the
latter, but for the former it may be due to differences in the way the
[\ion{O}{iii}] doublet emission is accounted for. {\bf (In both cases,
  the offsets are smaller than $3\sigma$, in the sense that the stated
  offset is less than $3$ times the stated dispersion. The offsets are
  thus not really significant... is this discussion therefore really
  worth it? A number of other indices from \citealt{Rampazzo2005} also
  show equally significant offsets ($\approx2\sigma$). What about
  them? I think this notion of the ``significance'' of the offsets
  must be introduced/addressed to justify which offsets you choose to
  discuss.)}

Indices other than G4300 and Fe5015 generally have literature
measurements that are fairly consistent with ours, although the
dispersions of the measurements are fairly large (perhaps due to the
transformations from Lick to LIS system indices).

{\bf (A number of the offsets listed in the table actually {\em are}
  significant (i.e.\ $>3\sigma$). In particular, a majority of the
  offsets with the \citealt{Ogando2008} measurements are
  significant. Why are these measurements so inconsistent? I think
  this should be discussed.)}

@@

Assuming that the individual spectra from our Southern Sample galaxies
can be well approximated by a SSP, we use the methods and the
absorption line strength maps described in
Section~\ref{subsec:absorption} to produce maps of the most-likely SSP
parameters (see Appendix~\ref{sec:maps}): age ($t$), metallicity
($Z/H$) and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
  specify here (and presumably also in
  Section~\ref{subsubsec:stellarPop}) whether the stellar population
  parameters are mass- or luminosity-weighted.)}

@@

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs {\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
$\mathrm{[Fe/H]}=0.12\pm0.01$ for an aperture covering the central
$0.1$~kpc). {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr)
along the south-east branch of the molecular gas (\removed{white} 
\added{cyan} contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

\citet{Koleva2011} showed that while there are wide ranges of radial
gradients of age and metallicity across galaxy populations, the mean
gradients are approximately constant across a large mass range. To
probe this they assumed a linear relationship between $\log(t)$ or
[Fe/H] and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
considered are logarithmic radial gradients. We repeated these fits
with our Southern Sample galaxies, and the results are listed in
Table~\ref{tab:derivedProp}.

\begin{table*}
  \begin{center}
    \caption{Derived stellar population and ionised gas properties of
      our Southern Sample galaxies.}
    \label{tab:derivedProp}
    \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c}
      \hline
      \hline 
      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{$\Delta\text{[Fe/H]}$} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec. & Ionisation\\
             & VIMOS & MUSE & VIMOS & MUSE & VIMOS$^\text{a}$ & MUSE & & \\
      \hline
      ESO~443-G024 & $0.019\pm0.013$ & -- & $-0.01\pm0.02$ & -- & $5.02\pm0.01$ & -- & -- & LINER \\
      IC~1459 & $0.005\pm0.015$ & $0.003\pm0.002$ & $-0.02\pm0.02$ & $0.00\pm0.06$ & $5.21\pm0.01$ & $5.50\pm0.01$ & $4.54\pm0.12$ & LINER-AGN \\
      IC~1531 & $0.012\pm0.015$ & -- & $\leavevmode\phantom{-}0.01\pm0.02$ & -- & $5.09\pm0.01$ & -- & -- & Seyfert 2\\
      IC~4296 & $0.012\pm0.010$ & $0.000\pm0.002$ & $-0.03\pm0.01$ & $0.04\pm0.08$ & $5.43\pm0.01$ & $< 4.48$ & $^\text{b}$ & LINER-AGN \\
      NGC~612 & $0.068\pm0.060$ & -- & $-0.11\pm0.02$ & -- & $6.00\pm0.01$ & --	& -- & LINER-AGN \\
      NGC~1316 & -- & $0.001\pm0.002$ & -- &$0.05\pm0.03$ & -- & $ 5.29\pm0.01$ & $3.52\pm0.11$ & LINER-AGN \\
      NGC~1399 & $0.019\pm0.005$ & $0.001\pm0.002$ & $-0.02\pm0.03$ & $0.10\pm0.09$ & $< 3.86$ & $ 4.54\pm0.01$ & $< 21.4^\text{c}$ & LINER \\
      NGC~3100 & $0.000\pm0.010$ & -- & $-0.06\pm0.01$ & -- & $5.26\pm0.01$ & -- & -- & LINER-AGN \\
      NGC~3557 & $0.048\pm0.039$ & -- & $-0.05\pm0.05$ & -- & $4.61\pm0.02$ & -- & -- & LINER \\
      NGC~7075 & $0.007\pm0.011$ & -- & $-0.07\pm0.02$ & -- & $4.68\pm0.01$ & -- & -- & LINER \\
      PKS~718-34 & $0.002\pm0.009$ & -- & $-0.17\pm0.03$ & -- & $< 5.08$ & -- & -- & Passive \\
      \hline
      \hline
    \end{tabular*}
    \parbox[t]{0.95\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Cols.~2\,--\,3: logarithmic radial age gradient of
      the most-likely SSP model. Cols.~4\,--\,5: logarithmic radial
      metallicity gradient of the most-likely SSP
      model. Cols.~6\,--\,7: \ion{H}{ii} mass derived from the
      H$\beta$ (assuming a Balmer decrement of $2.85$) or H$\alpha$
      line for the VIMOS or MUSE data, respectively. Col.~8: Balmer
      decrement measured from the MUSE data. Col.~9: Primary
      ionisation mechanism (see Section~\ref{subsec:Diagnostics} for a
      description of the different mechanisms).\\
      $^\text{a}$ The VIMOS flux calibration and thus the derived
      \ion{H}{ii} masses are only approximate (see
      Section~\ref{sec:obs} for more detail on the flux
      calibration).\\
      $^\text{b}$ Neither H$\alpha$ nor H$\beta$ is detected with
      $A/N>2.5$, so no useful Balmer decrement can be measured.\\
      $^\text{c}$ H$\beta$ is not detected with $A/N>2.5$, so the fit
      is unreliable and only an upper limit on the Balmer decrement
      (assuming an H$\beta$ detection with $A/N=2.5$) is reported.}
  \end{center}
\end{table*}

We find average logarithmic radial gradients of
$\Delta\log(t)=0.014\pm0.007$ and
$\Delta\text{[Fe/H]}=-0.03\pm0.01$. These are consistent with the
results of \citet{Koleva2011}, who found average gradients of
respectively $0.06\pm0.09$ and $-0.26\pm0.08$ for elliptical galaxies,
and respectively $0.01\pm0.11$ and $-0.12\pm0.13$ (i.e.\ flatter) for
lenticular galaxies.

@@

Radio-loud S0 galaxies are extremely rare, with only a handful of
known cases \citep[e.g.][]{Heckman1982, Morganti2011}. This is
presumably due to the mass functions of S0s and radio galaxies,
massive S0s and low-mass radio galaxies both being rare, with similar
transition masses from rare to more numerous. NGC~612 is one of those
rare cases. {\bf (You are not discussing here any of your own results,
  just rehashing old knowledge, so unless you have something else to
  say about NGC~612 (from your own work), I would suggest to remove
  this paragraph entirely (and/or certainly move it somewhere else
  more relevant).)}

>>>>

\begin{table*}[t]
  \begin{center}
    % \begin{threeparttable}
    \caption{Key characteristics of our Southern Sample galaxies.}
    \label{tab:sample}
    \begin{tabular*}{0.7\textwidth}{@{\extracolsep{\fill}}l c c c c l}
      \hline
      \hline
      Host galaxy & Radio source & Redshift & $S_\text{1.4\,GHz}$ & $m_K$ & Dust morphology\\
                  & (PKS) & & (mJy) & (mag) &\\
      \hline 
      ESO~443-G024 & 1258-321 & $0.01703$ & $1387\pm45$ & $8.51$ & no dust$^\text{a}$\\ 
      IC~1459 & 2254-367 & $0.00565$ & $1280\pm45$ & $6.81$ & dust lane$^\text{b}$\\
      IC~1531 & 0007-325 & $0.02553$ & $\leavevmode\phantom{0}388\pm12$ & $9.55$ & --\\
      IC~4296 & 1333-\leavevmode\phantom{0}33 & $0.01248$	& $1342\pm41$ & $7.50$ & edge-on disc$^\text{b}$\\
      NGC~612 & 0131-\leavevmode\phantom{0}36 & $0.02954$ & $\leavevmode\phantom{0}585\pm18$ & $9.58$ & dust lane$^\text{c}$\\
      NGC~1316 & 0320-\leavevmode\phantom{0}37 & $0.00591$ & $\leavevmode\phantom{0}255\pm10$ & $5.59$ & dust patches$^\text{b}$\\
      NGC~1399 & 0336-\leavevmode\phantom{0}35 & $0.00472$ & $\leavevmode\phantom{0}209\pm\leavevmode\phantom{0}7$ & $6.31$ & no dust$^\text{b}$\\
      NGC~3100 & 0958-314	& $0.00879$ & $\leavevmode\phantom{0}530\pm16$ & $8.08$ & dust lane$^\text{d}$\\
      NGC~3557 & 1107-372 & $0.01016$ & $\leavevmode\phantom{0}484\pm16$ & $7.20$ & face-on disc$^\text{b}$\\
      NGC~7075 & 2128-388 & $0.01819$ & $\leavevmode\phantom{0}837\pm28$ & $9.56$ & --\\
      -- & 0718-\leavevmode\phantom{0}34 & $0.02897$ & $1119\pm41$ & $9.97$ & dust patches$^\text{e}$\\
      \hline
      \hline
    \end{tabular*}
    % \begin{tablenotes}
    \parbox[t]{0.7\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Col.~2: radio source name from the Parkes Southern
      Radio Source Catalogue (PKS). We hereafter refer to the last
      galaxy by its PKS name only. Col.~3: redshift \added{(uncertainty in redshift is $< 0.00001$)}. Col.~4: National
      Radio Astronomy Observatory (NRAO) VLA Sky Survey (NVSS)
      $1.4$~GHz flux density \citep{Condon1998}. Col.~5: Two Micron
      All Sky Survey (2MASS) $K$-band apparent magnitude (with
      uncertainties of $\pm0.025$~mag;
      \citealt{Skrutskie2006}). Col.~6: dust morphology from (a)
      \citet{Govoni2000}, (b) \citet{Lauer2005}, (c)
      \citet{Bettoni2001}, (d) \citet{Sandage1979} and (e)
      \citet{Colbert2001}.}
    % \end{tablenotes}
    % \end{threeparttable}
  \end{center}
\end{table*}

@@

In each bin, using the measured absorption line strengths, we identify
the best-fitting \added{luminosity-weighted} single stellar population (SSP) model from an
interpolated grid of models using \textsc{emcee}, a \textsc{python}
affine-invariant Markov-chain Monte-Carlo (MCMC) fitting package
\citep{Foreman-Mackey2013}. This grid is created by linearly
interpolating between the models of \citeauthor{Thomas2010}
(\citeyear{Thomas2010}; hereafter \citetalias{Thomas2010}). The
\citetalias{Thomas2010} models are chosen because they are based on
high-resolution flux-calibrated spectra, and therefore do not require
the absorption line strength measurements to be in the Lick/IDS
system.

@@

We find $5$ out of $11$ galaxies, or $45\pm13\%$, are slow rotators
(see Fig.~\ref{fig:lambdaR_ellip}). This fraction is between that of
the Atlas$^\text{3D}$ and MASSIVE surveys, that find respectively
\added{$13\pm2\%$} and \added{$80\pm6\%$} of their sample galaxies to be slow
rotators. {\bf (Again, better to also quote the uncertainties on those
  two fractions. I doubt the decimal place is meaningful in either of
  them.)} As in the regular-/non-regular-rotator classification scheme
(Section~\ref{subsec:RR-NRR}), slow rotators are more likely to be
found in higher mass galaxies \added{(see lower panel of Fig.~\ref{fig:SRmassFraction})}, and the three samples
(Atlas$^\text{3D}$, MASSIVE and our Southern Sample) have very
different mass distributions (see the upper panel of
Fig.~\ref{fig:SRmassFraction}).

@@

We find a very large offset between the G4300 index measurements of
\citet{Rampazzo2005} and ours. This index is however extremely
sensitive to the stellar velocity dispersion correction, and we
measure an average difference of the stellar velocity dispersions
measured by \citet{Rampazzo2005} and us of $21$~km~s$^{-1}$. 
\removed{This may be enough to account for the offset of the measurements.} {\bf (Why not
  check this by changing the stellar velocity dispersions used in your
  corrections to those of \citealt{Rampazzo2005}? Check. JW: I can't get anywhere close the values of Rampazzo for G4300. Once the conversion to LIS is included, I have to double the stellar velocity dispersion, before I get can get similar results! I'm not sure what to do about this.)}

\removed{The offsets of our Fe5015 index measurements are also relatively large
when compared to the measurements of \citet{Rampazzo2005} and
\citet{Vazdekis2010}. The origin of this offset is unclear for the
latter, but for the former it may be due to differences in the way the
[\ion{O}{iii}] doublet emission is accounted for.} {\bf (In both cases,
  the offsets are smaller than $3\sigma$, in the sense that the stated
  offset is less than $3$ times the stated dispersion. The offsets are
  thus not really significant... is this discussion therefore really
  worth it? A number of other indices from \citealt{Rampazzo2005} also
  show equally significant offsets ($\approx2\sigma$). What about
  them? I think this notion of the ``significance'' of the offsets
  must be introduced/addressed to justify which offsets you choose to
  discuss.)}

\removed{Indices other than G4300 and Fe5015 generally have literature
measurements that are fairly consistent with ours, although the
dispersions of the measurements are fairly large (perhaps due to the
transformations from Lick to LIS system indices).}
{\bf (A number of the offsets listed in the table actually {\em are}
  significant (i.e.\ $>3\sigma$). In particular, a majority of the
  offsets with the \citealt{Ogando2008} measurements are
  significant. Why are these measurements so inconsistent? I think
  this should be discussed.)}

\added{For many indices \citet{Ogando2008} found significantly stronger measurements to us.} {\bf JW: I need help with this part, I don't know how to explain why they might be different - all I can say is that are.}

@@

Assuming that the individual spectra from our Southern Sample galaxies
can be well approximated by a SSP, we use the methods and the
absorption line strength maps described in
Section~\ref{subsec:absorption} to produce maps of the most-likely \added{luminosity-weighted} SSP
parameters (see Appendix~\ref{sec:maps}): age ($t$), metallicity
\removed{($Z/H$)}\added{($[M/H]$)} and alpha-element enhancement ($\alpha$/Fe). {\bf (You must
  specify here (and presumably also in
  Section~\ref{subsubsec:stellarPop}) whether the stellar population
  parameters are mass- or luminosity-weighted.)}

@@

In general, our Southern Sample galaxies show old, metal-rich and
alpha-enhanced SSPs, characteristics that are common in ETGs \added{\citep[e.g.][]{Worthey1992}}{\bf (Add
  a classic reference here.)} The exceptions are NGC~612 and
NGC~1316. NGC~1316 has a very young stellar population (our fit of
$t\approx2$~Gyr is consistent with that of \citealt{Kuntschner2000},
but is conflicting with the older and less metal-rich estimate of
\citealt{Koleva2011}, who found $t=4.5\pm0.3$~Gyr and
\removed{$\mathrm{[Fe/H]}=0.12\pm0.01$}\added{$\mathrm{[M/H]}=0.12\pm0.01$} \removed{for an aperture covering the central
$0.1$~kpc)}`added{using a long slit with width $1\arcsec$ and length $0.1$~kpc)}. {\bf (Is that a circular or square aperture? If circular,
  is $0.1$~kpc the radius or diameter? Clarify.)} We also find NGC~612
to have an extended young stellar population of
$t\approx4$~Gyr. Otherwise, NGC~3557 is notable for containing a
significantly younger ($t\approx4$~Gyr) core of $\approx10\arcsec$ in
diameter, and NGC~3100 has a branch of young stars ($t\approx4$\,Gyr) \added{with very high metallicity projecting southwards from below the eastern}
\removed{along the south-east} branch of the molecular gas (\removed{white} 
\added{cyan} contours in
Fig.~\ref{fig:ngc3100}). {\bf (I do not see the age feature you refer
  to in the NGC3100 maps, and the CO is distributed North-East to
  South-West, so there is no South-East CO ``branch''. Perhaps you
  meant South-West (where there is indeed a blue region in the
  H$\beta$ map, if not in the age map)? Also, there is no white
  contour in the figure. The CO contours are in pale
  blue/turquoise. Is that what you meant? In any case, this needs to
  be corrected to reflect the truth.)}

@@

\citet{Koleva2011} showed that while there are wide ranges of radial
gradients of age and metallicity across galaxy populations, the mean
gradients are approximately constant across a large mass range. To
probe this they assumed a linear relationship between $\log(t)$ or
\removed{[Fe/H]}\added{[M/H]} and $\log(R/R_\text{e})$, i.e.\ as is common the gradients
considered are logarithmic radial gradients. We repeated these fits
with our Southern Sample galaxies, and the results are listed in
Table~\ref{tab:derivedProp}.

\begin{table*}
  \begin{center}
    \caption{Derived stellar population and ionised gas properties of
      our Southern Sample galaxies.}
    \label{tab:derivedProp}
    \begin{tabular*}{0.95\textwidth}{@{\extracolsep{\fill}}l c c c c c c c c}
      \hline
      \hline 
      Galaxy & \multicolumn{2}{c}{$\Delta\log(t)$} & \multicolumn{2}{c}{\removed{$\Delta\text{[Fe/H]}$}\added{$\Delta\text{[M/H]}$}} & \multicolumn{2}{c}{$\log(M_\text{\ion{H}{ii}}/\mathrm{M_\odot})$} & Balmer Dec. & Ionisation\\
             & VIMOS & MUSE & VIMOS & MUSE & VIMOS$^\text{a}$ & MUSE & & \\
      \hline
      ESO~443-G024 & $0.019\pm0.013$ & -- & $-0.01\pm0.02$ & -- & $5.02\pm0.01$ & -- & -- & LINER \\
      IC~1459 & $0.005\pm0.015$ & $0.003\pm0.002$ & $-0.02\pm0.02$ & $0.00\pm0.06$ & $5.21\pm0.01$ & $5.50\pm0.01$ & $4.54\pm0.12$ & LINER-AGN \\
      IC~1531 & $0.012\pm0.015$ & -- & $\leavevmode\phantom{-}0.01\pm0.02$ & -- & $5.09\pm0.01$ & -- & -- & Seyfert 2\\
      IC~4296 & $0.012\pm0.010$ & $0.000\pm0.002$ & $-0.03\pm0.01$ & $0.04\pm0.08$ & $5.43\pm0.01$ & $< 4.48$ & $^\text{b}$ & LINER-AGN \\
      NGC~612 & $0.068\pm0.060$ & -- & $-0.11\pm0.02$ & -- & $6.00\pm0.01$ & --	& -- & LINER-AGN \\
      NGC~1316 & -- & $0.001\pm0.002$ & -- &$0.05\pm0.03$ & -- & $ 5.29\pm0.01$ & $3.52\pm0.11$ & LINER-AGN \\
      NGC~1399 & $0.019\pm0.005$ & $0.001\pm0.002$ & $-0.02\pm0.03$ & $0.10\pm0.09$ & $< 3.86$ & $ 4.54\pm0.01$ & $< 21.4^\text{c}$ & LINER \\
      NGC~3100 & $0.000\pm0.010$ & -- & $-0.06\pm0.01$ & -- & $5.26\pm0.01$ & -- & -- & LINER-AGN \\
      NGC~3557 & $0.048\pm0.039$ & -- & $-0.05\pm0.05$ & -- & $4.61\pm0.02$ & -- & -- & LINER \\
      NGC~7075 & $0.007\pm0.011$ & -- & $-0.07\pm0.02$ & -- & $4.68\pm0.01$ & -- & -- & LINER \\
      PKS~718-34 & $0.002\pm0.009$ & -- & $-0.17\pm0.03$ & -- & $< 5.08$ & -- & -- & Passive \\
      \hline
      \hline
    \end{tabular*}
    \parbox[t]{0.95\textwidth}{\footnotesize\textit{Notes:} Col.~1:
      galaxy name. Cols.~2\,--\,3: logarithmic radial age gradient of
      the most-likely SSP model. Cols.~4\,--\,5: logarithmic radial
      metallicity gradient of the most-likely SSP
      model. Cols.~6\,--\,7: \ion{H}{ii} mass derived from the
      H$\beta$ (assuming a Balmer decrement of $2.85$) or H$\alpha$
      line for the VIMOS or MUSE data, respectively. Col.~8: Balmer
      decrement measured from the MUSE data. Col.~9: Primary
      ionisation mechanism (see Section~\ref{subsec:Diagnostics} for a
      description of the different mechanisms).\\
      $^\text{a}$ The VIMOS flux calibration and thus the derived
      \ion{H}{ii} masses are only approximate (see
      Section~\ref{sec:obs} for more detail on the flux
      calibration).\\
      $^\text{b}$ Neither H$\alpha$ nor H$\beta$ is detected with
      $A/N>2.5$, so no useful Balmer decrement can be measured.\\
      $^\text{c}$ H$\beta$ is not detected with $A/N>2.5$, so the fit
      is unreliable and only an upper limit on the Balmer decrement
      (assuming an H$\beta$ detection with $A/N=2.5$) is reported.}
  \end{center}
\end{table*}

We find average logarithmic radial gradients of
$\Delta\log(t)=0.014\pm0.007$ and
\removed{$\Delta\text{[Fe/H]}=-0.03\pm0.01$}\added{$\Delta\text{[M/H]}=-0.03\pm0.01$}. These are consistent with the
results of \citet{Koleva2011}, who found average gradients of
respectively $0.06\pm0.09$ and $-0.26\pm0.08$ for elliptical galaxies,
and respectively $0.01\pm0.11$ and $-0.12\pm0.13$ (i.e.\ flatter) for
lenticular galaxies.

@@

\removed{Radio-loud S0 galaxies are extremely rare, with only a handful of
known cases \citep[e.g.][]{Heckman1982, Morganti2011}. This is
presumably due to the mass functions of S0s and radio galaxies,
massive S0s and low-mass radio galaxies both being rare, with similar
transition masses from rare to more numerous. NGC~612 is one of those
rare cases.} {\bf (You are not discussing here any of your own results,
  just rehashing old knowledge, so unless you have something else to
  say about NGC~612 (from your own work), I would suggest to remove
  this paragraph entirely (and/or certainly move it somewhere else
  more relevant).)}
